---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rdshub

<!-- badges: start -->
<!-- badges: end -->

The goal of {rdshub} is to provide a experimental functions for interacting with public-facing 'Dynamic Soils Hub' tools and APIs. Contents of this package may change at any time based on server-side changes and new approaches. Well-polished functions may be moved to other packages eventually.

Currently the following functions are available:

 - `dsh_soil_properties()`


## Installation

You can install the development version of rdshub from [GitHub](https://github.com/brownag/rdshub) with:

``` r
# install.packages("remotes")
remotes::install_github("brownag/rdshub")
```

## Example

This is a basic example demonstrating how to obtain variables with top depth `0` cm, and bottom depth `0` cm and `200` cm. 

The result includes all "site" level variables that have a `"domcond"` (dominant condition) aggregation, as well as all `"wtdavg"` (depth weighted average) variables for interval `[0,200]`

```{r example}
library(rdshub)
library(terra)

x <- dsh_soil_properties(
  # variables = c("claytotal", "sandtotal", "silttotal", "drainagecl"),
  top_depth = 0,
  bottom_depth = c(0, 200),
  aggregations = c("wtdavg", "domcond"),
  resolutions = 900
)

terra::sources(x)

terra::metags(x, layer = 1)

vars <- x |>
  terra::metags(seq_len(terra::nlyr(x))) |>
  subset(name == "variable")
names(x) <- vars$value

terra::plot(x)

x$sandtotal + x$claytotal + x$silttotal
```
